Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-04-11 2016-Weak-FH-Bisim/WeakBisim.tex
clarify substraction
def 11 updated

$\uplus$ is the disjoint operator on sets. We extend it to  disjoint union  of indexed 
sets defined by the merge of the 
two sets provided they are indexed on disjoint families.
The elements
of the union of two indexed sets are then accessed by using an index of one of the two
joined families.
%We suppose here that disjoint unions are always well defined; this
%requires to choose disjoint  
%indices in the definition of the component system (e.g. name of
%methods of different interfaces).
$\setminus$ is the standard subtraction operation on sets.

@@

Intuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
We define $\Id(s)$ as the identity function on variables of state s.
\begin{definition}[Non-observability of silent actions]\label{def:Non-ObsTau}
An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
\begin{enumerate}
\item
\[ \openrule
         {
           (j\mapsto\tau),\True,\Id(s)}
         {s \OTarrow {\tau} s}
         \in \mathcal{T}
\]
and 
\item for all $A$, $\alpha$,  $s$, $\Post$ and $s'$ such that
\[ \openrule
         {
           A,\Pred,\Post}
         {s \OTarrow {\alpha} s'}
         \in \mathcal{T} \] If there is a $j$ such that $A(j)=\tau$ then we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s)
\]
\end{enumerate}
\end{definition}
The first statement of the definition state that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e. cannot change its internal state because a hole did a $\tau$ transition. The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a silent action from a hole.

>>>>

$\uplus$ is the disjoint union on sets. We extend it to  disjoint union  of indexed 
sets defined by the merge of the 
two sets provided they are indexed on disjoint families.
The elements
of the union of two indexed sets are then accessed by using an index of one of the two
joined families.
%We suppose here that disjoint unions are always well defined; this
%requires to choose disjoint  
%indices in the definition of the component system (e.g. name of
%methods of different interfaces).
$\setminus$ is the standard subtraction operation on indexed sets: $\dom(A\setminus B)=\dom(A)\setminus B$.

@@

Intuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
We define $\Id(s)$ as the identity function on variables of state s.
\begin{definition}[Non-observability of silent actions]\label{def:Non-ObsTau}
An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
\begin{enumerate}
\item
\[ \openrule
         {
           (j\mapsto\tau),\True,\Id(s)}
         {s \OTarrow {\tau} s}
         \in \mathcal{T}
\]
and 
\item for all $A$, $\alpha$,  $s$, $\Post$ and $s'$ such that
\[ \openrule
         {
           A,\Pred,\Post}
         {s \OTarrow {\alpha} s'}
         \in \mathcal{T} \] If there is a $j$ such that $A(j)=\tau$ then we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s) \land A=(j\mapsto \tau)
\]
\end{enumerate}
\end{definition}
The first statement of the definition state that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e. cannot change its internal state because a hole did a $\tau$ transition. The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a silent action from a hole. The condition $A=(j\mapsto \tau)$ is a bit restrictive, it could safely be replaced by $\forall h\in\dom(A).\, A(h)=\tau$, allowing the other holes to perform silent transitions too (because these silent actions cannot be observed).
